\documentclass[a4paper,12pt]{article}

\usepackage{amsmath}
\usepackage[margin=1in]{geometry}

\title{Electrical Power Worksheet}
\author{}
\date{}

\begin{document}

\maketitle

\[
P = IV \qquad
P = I^2 R \qquad
P = \frac{V^2}{R}
\]

\begin{enumerate}

\item A device operates with a current of 3\,A and a potential difference of 12\,V. Calculate the power dissipated.

\item A resistor has a potential difference of 9\,V across it and carries a current of 2\,A. Calculate the power.

\item A heater draws a current of 5\,A from a 240\,V supply. Calculate its power rating.

\item A circuit component dissipates 60\,W of power when a current of 4\,A flows through it. Calculate the potential difference across it.

\item A lamp is rated at 24\,W when connected to a 12\,V supply. Calculate the current drawn.

\item A resistor of resistance 10\,$\Omega$ carries a current of 2\,A. Calculate the power dissipated.

\item A current of 0.5\,A flows through a 20\,$\Omega$ resistor. Calculate the power dissipated.

\item A resistor dissipates 45\,W of power. If its resistance is 5\,$\Omega$, calculate the current.

\item A wire of resistance 8\,$\Omega$ dissipates 32\,W of power. Calculate the current through the wire.

\item A resistor of 4\,$\Omega$ carries a current that produces 64\,W of power. Calculate the current.

\item A resistor has a potential difference of 10\,V across it and a resistance of 5\,$\Omega$. Calculate the power.

\item A 6\,$\Omega$ resistor has 12\,V across it. Calculate the power dissipated.

\item A resistor dissipates 50\,W when connected across a 25\,V supply. Calculate its resistance.

\item A component has a power dissipation of 18\,W when a potential difference of 9\,V is applied. Calculate the resistance.

\item A resistor of unknown resistance dissipates 100\,W when 20\,V is applied. Find the resistance.

\item A device draws 2\,A from a 12\,V supply. Calculate its resistance and power.

\item A resistor dissipates 72\,W when a current of 3\,A flows through it. Calculate its resistance and the potential difference across it.

\item A 10\,$\Omega$ resistor is connected to a 20\,V supply. Calculate the current and the power dissipated.

\item A resistor has a resistance of 15\,$\Omega$ and dissipates 60\,W of power. Calculate the current and voltage.

\item A device operates at 48\,W when connected to a 24\,V supply. Calculate the current and resistance.

\item A wire of resistance 2\,$\Omega$ carries a current of 6\,A. Calculate the power dissipated.

\item A heater rated at 2\,kW is connected to a 250\,V supply. Calculate the current drawn.

\item A 100\,W bulb operates on a 200\,V supply. Calculate its resistance.

\item A resistor of 25\,$\Omega$ is connected to a 50\,V supply. Calculate the current and power.

\item A component dissipates 80\,W when a current of 4\,A flows through it. Calculate its resistance and potential difference.

\item A 12\,V battery supplies a current of 3\,A to a resistor. Calculate the power and resistance.

\item A resistor dissipates 36\,W when connected to a 12\,V supply. Calculate the current and resistance.

\item A resistor has a resistance of 50\,$\Omega$ and dissipates 200\,W. Calculate the current and voltage.

\item A 5\,$\Omega$ resistor is connected to a supply and dissipates 125\,W. Calculate the current and voltage.

\item A component draws 0.2\,A from a 230\,V supply. Calculate the power and resistance.

\end{enumerate}

\newpage

\section*{Answer Key}

\begin{enumerate}

\item $36\,\text{W}$
\item $18\,\text{W}$
\item $1200\,\text{W}$
\item $15\,\text{V}$
\item $2\,\text{A}$
\item $40\,\text{W}$
\item $5\,\text{W}$
\item $3\,\text{A}$
\item $2\,\text{A}$
\item $4\,\text{A}$
\item $20\,\text{W}$
\item $24\,\text{W}$
\item $12.5\,\Omega$
\item $4.5\,\Omega$
\item $4\,\Omega$
\item $6\,\Omega,\; 24\,\text{W}$
\item $8\,\Omega,\; 24\,\text{V}$
\item $2\,\text{A},\; 40\,\text{W}$
\item $2\,\text{A},\; 30\,\text{V}$
\item $2\,\text{A},\; 12\,\Omega$
\item $72\,\text{W}$
\item $8\,\text{A}$
\item $400\,\Omega$
\item $2\,\text{A},\; 100\,\text{W}$
\item $5\,\Omega,\; 20\,\text{V}$
\item $36\,\text{W},\; 4\,\Omega$
\item $3\,\text{A},\; 4\,\Omega$
\item $2\,\text{A},\; 100\,\text{V}$
\item $5\,\text{A},\; 25\,\text{V}$
\item $46\,\text{W},\; 1150\,\Omega$

\end{enumerate}

\end{document}